---
title: "expressalyzr Analysis Report"
date: "`r Sys.Date()`"
output:
  html_document:
    self_contained: true
    toc: true
    toc_float: true
    theme: flatly
params:
  experiment_name: "experiment"
  data_path: "."
  gs: NULL
  qc_results: NULL
  so_mat: NULL
  gating_results: NULL
  data_dt: NULL
  population_table: NULL
  marker_table: NULL
  save_gating_set: false
  summaries_written: false
  include_gating_plots: false
  gg_theme: "minimal"
  max_events: 5000
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE, warning = FALSE, message = FALSE,
  fig.width = 10, fig.height = 5, dpi = 150,
  dev = "png", dev.args = list(bg = "transparent")
)
library(data.table)
library(ggplot2)

base_pal <- expressalyzr::expressalyzr_palette()
pal <- list(
  ok = base_pal[["green"]],
  warn = base_pal[["coral"]],
  fill = base_pal[["teal"]],
  mute = base_pal[["muted"]],
  grid = base_pal[["grid"]],
  panel = base_pal[["panel"]],
  ink = base_pal[["ink"]],
  blue = base_pal[["blue"]]
)

theme_qc <- function(base_size = 11) {
  expressalyzr::theme_expressalyzr(base_size = base_size) +
    theme(legend.position = "bottom")
}
theme_set(theme_qc())

fmt_number <- function(x, digits = 0) {
  format(round(x, digits), big.mark = ",", scientific = FALSE)
}

qc_table_labels <- c(
  sample = "Sample",
  population = "Population",
  count = "Count",
  parent_pct = "% Parent",
  gating_template = "Template",
  gated_population = "Gated Population",
  channel = "Channel",
  mean = "Mean",
  median = "Median",
  sd = "SD",
  cv = "CV (%)",
  pct_positive = "% Positive",
  dynamic_range = "Dynamic Range",
  time_bin = "Time Bin",
  event_count = "Event Count"
)

qc_kable <- function(x, columns = names(x), digits = 1, include_extra = TRUE) {
  x <- as.data.table(x)
  columns <- intersect(columns, names(x))
  if (isTRUE(include_extra)) {
    columns <- unique(c(columns, setdiff(names(x), columns)))
  }
  labels <- unname(ifelse(
    columns %in% names(qc_table_labels),
    qc_table_labels[columns],
    columns
  ))
  knitr::kable(
    x[, columns, with = FALSE],
    digits = digits,
    format = "html",
    col.names = labels,
    table.attr = 'class="table table-striped table-hover table-sm"'
  )
}

flag_outliers <- expressalyzr::flag_outliers

ec        <- params$qc_results$event_counts
ss        <- params$qc_results$scatter_stats
cs_stats  <- params$qc_results$channel_stats
gs        <- params$gs
data_dt   <- params$data_dt
population_table <- params$population_table
marker_table <- params$marker_table
samples   <- unique(ec$sample)
n_samples <- length(samples)
detail_mode <- n_samples <= 24
gate_plot_columns <- 4L
gate_samples_per_page <- gate_plot_columns * 3L
gating_context <- params$gating_results
if (is.null(gating_context)) {
  gating_context <- list(list(
    label = "default",
    population_label = "singlets",
    gs = gs
  ))
}

context_label <- function(result) {
  population <- result$population_label
  template <- result$label
  if (is.null(population) || is.na(population) || !nzchar(population)) {
    population <- template
  }
  if (is.null(population) || is.na(population) || !nzchar(population)) {
    population <- "default"
  }
  population
}

context_template <- function(result) {
  template <- result$label
  if (is.null(template) || is.na(template) || !nzchar(template)) {
    template <- "gt_samples"
  }
  template
}

default_gated_population <- function() {
  if (length(gating_context) > 0L) {
    return(context_label(gating_context[[1L]]))
  }
  "default"
}

ensure_gated_population <- function(x, default_label = default_gated_population()) {
  if (is.null(x)) {
    return(data.table())
  }
  dt <- as.data.table(copy(x))
  if (!"gated_population" %in% names(dt)) {
    dt[, "gated_population" := default_label]
  }
  missing_label <- is.na(dt[["gated_population"]]) |
    !nzchar(dt[["gated_population"]])
  dt[missing_label, "gated_population" := default_label]
  dt
}

split_by_gated_population <- function(x, default_label = default_gated_population()) {
  dt <- ensure_gated_population(x, default_label = default_label)
  if (nrow(dt) == 0L) {
    return(list())
  }
  labels <- unique(dt$gated_population)
  stats::setNames(
    lapply(labels, function(label) dt[dt[["gated_population"]] == label]),
    labels
  )
}

section_heading <- function(label, level = 4L) {
  cat(paste0("\n\n", paste(rep("#", level), collapse = ""), " ", label, "\n\n"))
}

ec <- ensure_gated_population(ec)
ss <- ensure_gated_population(ss)
cs_stats <- ensure_gated_population(cs_stats)

# Pre-compute outlier flags for the summary banner
ec_flags <- ec[population != "root" & !is.na(parent_pct),
               .(outlier = flag_outliers(parent_pct)),
               by = .(gated_population, population)]
n_ec_flagged <- sum(ec_flags$outlier)

ss_flags <- ss[, .(outlier = flag_outliers(cv)),
               by = .(gated_population, channel)]
n_ss_flagged <- sum(ss_flags$outlier)

n_cs_flagged <- 0L
if (nrow(cs_stats) > 0) {
  cs_flags <- cs_stats[, .(outlier = flag_outliers(median)),
                       by = .(gated_population, channel)]
  n_cs_flagged <- sum(cs_flags$outlier)
}

status_icon <- function(n) {
  paste0('<span style="font-weight:bold;">', fmt_number(n), '</span>')
}

compact_gate_axis <- scale_x_continuous(
  labels = scales::label_scientific(digits = 2),
  breaks = scales::breaks_extended(n = 3),
  guide = guide_axis(check.overlap = TRUE)
)

compact_gate_y_axis <- scale_y_continuous(
  labels = scales::label_scientific(digits = 2),
  breaks = scales::breaks_extended(n = 3),
  guide = guide_axis(check.overlap = TRUE)
)
```

# `r params$experiment_name`

> **`r n_samples` samples** &middot;
`r fmt_number(ec[population == "root", sum(count)])` total events &middot;
`r Sys.Date()`

### QC Summary

| Metric | Flagged Samples |
|:-------|:---------------:|
| Event Counts | `r status_icon(n_ec_flagged)` |
| Scatter Quality | `r status_icon(n_ss_flagged)` |
| Channel Distributions | `r status_icon(n_cs_flagged)` |

```{r template-summary, results='asis'}
template_summary <- rbindlist(lapply(gating_context, function(result) {
  data.table(
    gated_population = context_label(result),
    gating_template = context_template(result),
    samples = length(flowWorkspace::sampleNames(result$gs)),
    populations = length(flowWorkspace::gs_get_pop_paths(result$gs, path = "auto")) - 1L
  )
}))

if (nrow(template_summary) > 1L) {
  cat("\n\n### Gating Templates\n\n")
  qc_kable(template_summary, digits = 0)
}

if (!is.null(data_dt) && all(c("gated_population", "File") %in% names(data_dt))) {
  pop_counts <- as.data.table(data_dt)[, .(events = .N), by = .(gated_population, File)]
  pop_summary <- pop_counts[, .(
    samples = uniqueN(File),
    median_events = stats::median(events),
    min_events = min(events),
    max_events = max(events)
  ), by = gated_population]
  if (nrow(pop_summary) > 1L) {
    cat("\n\n### Exported Events by Gated Population\n\n")
    qc_kable(pop_summary, digits = 0)
  }
}
```

---

## Event Counts {.tabset}

Distribution of parent-gate retention (%) across all samples. Each point is one
sample; red points are outliers (> 2 MAD from median).

### Distribution

```{r event-counts-dist, fig.height=4, results='asis'}
ec_plot_all <- ec[population != "root" & !is.na(parent_pct)]
event_count_groups <- split_by_gated_population(ec_plot_all)

if (length(event_count_groups) == 0L) {
  cat("No event-count QC rows available.")
} else {
  for (label in names(event_count_groups)) {
    section_heading(label)
    ec_plot <- copy(event_count_groups[[label]])
    ec_plot[, population := factor(population, levels = unique(population))]
    ec_plot[, outlier := flag_outliers(parent_pct), by = population]

    print(
      ggplot(ec_plot, aes(x = parent_pct, y = population)) +
        geom_boxplot(fill = pal$panel, colour = pal$mute, outlier.shape = NA, width = 0.5) +
        geom_jitter(aes(colour = outlier), height = 0.15, size = 1.8, alpha = 0.8) +
        scale_colour_manual(values = c("FALSE" = pal$fill, "TRUE" = pal$warn),
                            labels = c("Normal", "Outlier"), name = NULL) +
        labs(x = "% of Parent Gate", y = NULL,
             title = paste(label, "Gate Retention"),
             subtitle = paste(uniqueN(ec_plot$sample), "samples")) +
        theme(legend.position = "top")
    )
  }
}
```

### Flagged

```{r event-counts-flagged, results='asis'}
event_count_groups <- split_by_gated_population(
  ec[population != "root" & !is.na(parent_pct)]
)

if (length(event_count_groups) == 0L) {
  cat("No event-count QC rows available.")
} else {
  for (label in names(event_count_groups)) {
    section_heading(label)
    ec_flagged <- copy(event_count_groups[[label]])
    ec_flagged[, outlier := flag_outliers(parent_pct), by = population]
    ec_flagged <- ec_flagged[outlier == TRUE]

    if (nrow(ec_flagged) > 0) {
      print(qc_kable(
        ec_flagged,
        columns = c("gating_template", "gated_population", "sample", "population",
                    "parent_pct", "count"),
        digits = 1,
        include_extra = FALSE
      ))
    } else {
      cat("No outliers detected.\n\n")
    }
  }
}
```

### Full Data

```{r event-counts-table, results='asis'}
event_count_groups <- split_by_gated_population(ec)

for (label in names(event_count_groups)) {
  section_heading(label)
  ec_display <- copy(event_count_groups[[label]])
  ec_display[, count := fmt_number(count)]
  print(qc_kable(
    ec_display,
    columns = c("gating_template", "gated_population", "sample", "population",
                "count", "parent_pct"),
    digits = 1
  ))
}
```

## {-}

---

## Scatter Quality {.tabset}

Coefficient of variation (CV) of FSC-A and SSC-A across all samples.
Red points indicate outlier CVs (> 2 MAD from median).

### Distribution

```{r scatter-dist, fig.height=4, results='asis'}
scatter_groups <- split_by_gated_population(ss)

if (length(scatter_groups) == 0L) {
  cat("No scatter QC rows available.")
} else {
  for (label in names(scatter_groups)) {
    section_heading(label)
    ss_plot <- copy(scatter_groups[[label]])
    ss_plot[, outlier := flag_outliers(cv), by = channel]

    print(
      ggplot(ss_plot, aes(x = cv, y = channel)) +
        geom_boxplot(fill = pal$panel, colour = pal$mute, outlier.shape = NA, width = 0.4) +
        geom_jitter(aes(colour = outlier), height = 0.1, size = 2, alpha = 0.8) +
        scale_colour_manual(values = c("FALSE" = pal$fill, "TRUE" = pal$warn),
                            labels = c("Normal", "Outlier"), name = NULL) +
        labs(x = "CV (%)", y = NULL,
             title = paste(label, "Scatter CV"),
             subtitle = paste(uniqueN(ss_plot$sample), "samples")) +
        theme(legend.position = "top")
    )
  }
}
```

### Flagged

```{r scatter-flagged, results='asis'}
scatter_groups <- split_by_gated_population(ss)

if (length(scatter_groups) == 0L) {
  cat("No scatter QC rows available.")
} else {
  for (label in names(scatter_groups)) {
    section_heading(label)
    ss_flag <- copy(scatter_groups[[label]])
    ss_flag[, outlier := flag_outliers(cv), by = channel]
    ss_flag <- ss_flag[outlier == TRUE]

    if (nrow(ss_flag) > 0) {
      print(qc_kable(
        ss_flag,
        columns = c("gating_template", "gated_population", "sample", "channel",
                    "cv", "mean", "median"),
        digits = 1,
        include_extra = FALSE
      ))
    } else {
      cat("No outliers detected.\n\n")
    }
  }
}
```

```{r scatter-detail, fig.width=12, fig.height=max(4, 3.5 * ceiling(min(n_samples, 24) / 4)), eval=detail_mode && length(gating_context) > 0, results='asis'}
max_ev <- params$max_events

for (result in gating_context) {
  section_heading(context_label(result))
  gs <- result$gs
  pops <- flowWorkspace::gs_get_pop_paths(gs, path = "auto")
  root_pop <- pops[1]
  result_samples <- flowWorkspace::sampleNames(gs)

  scatter_rows <- lapply(result_samples, function(s) {
    cf  <- flowWorkspace::gh_pop_get_data(gs[[s]], y = root_pop)
    mat <- flowCore::exprs(cf)
    avail <- intersect(c("FSC-A", "SSC-A"), colnames(mat))
    if (length(avail) == 2) {
      dt <- as.data.table(mat[, avail])
      if (nrow(dt) > max_ev) dt <- dt[sample(.N, max_ev)]
      dt[, sample := s]
      dt
    }
  })
  scatter_dt <- rbindlist(Filter(Negate(is.null), scatter_rows))

  if (nrow(scatter_dt) > 0) {
    print(
      ggplot(scatter_dt, aes(x = `FSC-A`, y = `SSC-A`)) +
        geom_hex(bins = 80, na.rm = TRUE) +
        scale_fill_gradientn(
          colours = c(pal$panel, pal$fill, pal$ink),
          trans = "log10",
          name = "Count"
        ) +
        facet_wrap(~ sample, ncol = 4, scales = "fixed") +
        labs(x = "FSC-A", y = "SSC-A",
             title = paste(context_label(result), "Scatter Detail (downsampled)")) +
        theme(aspect.ratio = 1, strip.text = element_text(size = 8))
    )
  }
}
```

### Full Data

```{r scatter-table, results='asis'}
scatter_groups <- split_by_gated_population(ss)

for (label in names(scatter_groups)) {
  section_heading(label)
  ss_display <- copy(scatter_groups[[label]])
  ss_display[, `:=`(mean = fmt_number(mean), median = fmt_number(median),
                     sd = fmt_number(sd))]
  print(qc_kable(
    ss_display,
    columns = c("gating_template", "gated_population", "sample", "channel",
                "mean", "median", "sd", "cv"),
    digits = 1
  ))
}
```

## {-}

---

## Channel Distributions {.tabset}

Median fluorescence intensity per channel across all samples.
Each point is one sample; red points are outliers (> 2 MAD from median).

### Distribution

```{r channel-dist, fig.height=max(3, 0.8 * length(unique(cs_stats$channel))), results='asis'}
channel_groups <- split_by_gated_population(cs_stats)

if (length(channel_groups) > 0L) {
  for (label in names(channel_groups)) {
    section_heading(label)
    cs_plot <- copy(channel_groups[[label]])
    cs_plot[, outlier := flag_outliers(median), by = channel]

    print(
      ggplot(cs_plot, aes(x = median, y = channel)) +
        geom_boxplot(fill = pal$panel, colour = pal$mute, outlier.shape = NA, width = 0.5) +
        geom_jitter(aes(colour = outlier), height = 0.12, size = 1.8, alpha = 0.8) +
        scale_colour_manual(values = c("FALSE" = pal$fill, "TRUE" = pal$warn),
                            labels = c("Normal", "Outlier"), name = NULL) +
        scale_x_log10(labels = scales::label_comma()) +
        labs(x = "Median Intensity (log scale)", y = NULL,
             title = paste(label, "Channel Median Intensity"),
             subtitle = paste(uniqueN(cs_plot$sample), "samples")) +
        theme(legend.position = "top")
    )
  }
} else {
  cat("No fluorescence channel data available.")
}
```

### Flagged

```{r channel-flagged, results='asis'}
channel_groups <- split_by_gated_population(cs_stats)

if (length(channel_groups) > 0L) {
  for (label in names(channel_groups)) {
    section_heading(label)
    cs_flag <- copy(channel_groups[[label]])
    cs_flag[, outlier_med := flag_outliers(median), by = channel]
    cs_flag[, outlier_cv  := flag_outliers(cv), by = channel]
    cs_flag <- cs_flag[outlier_med == TRUE | outlier_cv == TRUE]

    if (nrow(cs_flag) > 0) {
      print(qc_kable(
        cs_flag,
        columns = c("gating_template", "gated_population", "sample", "channel",
                    "median", "cv", "pct_positive"),
        digits = 1,
        include_extra = FALSE
      ))
    } else {
      cat("No outliers detected.\n\n")
    }
  }
} else {
  cat("No fluorescence channel data available.")
}
```

```{r channel-violins, fig.width=12, fig.height=max(3, 1.5 * length(unique(cs_stats$channel))), eval=detail_mode && !is.null(data_dt)}
tryCatch({
  fl_dt <- as.data.table(copy(data_dt))
  fl_chs <- colnames(fl_dt)[grepl("^FL", colnames(fl_dt))]

  if (length(fl_chs) > 0) {
    max_ev <- params$max_events
    sample_by <- intersect(c("gated_population", "File"), names(fl_dt))
    if (length(sample_by) == 0L) sample_by <- "File"
    if (nrow(fl_dt) / max(1, uniqueN(fl_dt$File)) > max_ev) {
      fl_dt <- fl_dt[, .SD[sample(.N, min(.N, max_ev))], by = sample_by]
    }

    id_cols <- intersect(c("gated_population", "File"), names(fl_dt))
    tall <- melt(fl_dt, id.vars = id_cols, measure.vars = fl_chs,
                 variable.name = "Channel", value.name = "Intensity")
    tall <- tall[Intensity > 0]
    if (!"gated_population" %in% names(tall)) {
      tall[, gated_population := "singlets"]
    }

    violin_groups <- split_by_gated_population(tall)
    for (label in names(violin_groups)) {
      section_heading(label)
      tall_pop <- violin_groups[[label]]
      print(
        ggplot(tall_pop, aes(x = File, y = Intensity)) +
          geom_violin(fill = pal$fill, colour = NA, alpha = 0.5, scale = "width") +
          geom_boxplot(width = 0.15, outlier.size = 0.3, fill = pal$panel,
                       colour = pal$mute) +
          scale_y_log10(labels = scales::label_comma()) +
          facet_wrap(~ Channel, scales = "free_y") +
          labs(x = NULL, y = "Intensity (log scale)",
               title = paste(label, "Per-Sample Distributions (detail)")) +
          theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 7))
      )
    }
  }
}, error = function(e) invisible(NULL))
```

### Full Data

```{r channel-table, results='asis'}
channel_groups <- split_by_gated_population(cs_stats)

if (length(channel_groups) > 0L) {
  for (label in names(channel_groups)) {
    section_heading(label)
    cs_display <- copy(channel_groups[[label]])
    cs_display[, `:=`(mean = fmt_number(mean, 1), median = fmt_number(median, 1),
                       sd = fmt_number(sd, 1))]
    print(qc_kable(
      cs_display,
      columns = c("gating_template", "gated_population", "sample", "channel",
                  "mean", "median", "sd", "cv", "pct_positive",
                  "dynamic_range"),
      digits = 1
    ))
  }
} else {
  cat("No fluorescence channel data available.")
}
```

## {-}

---

## Gating

```{r gating-hierarchy, results='asis', fig.width=10, fig.height=6, eval=length(gating_context) > 0}
for (result in gating_context) {
  cat(paste0("\n\n### ", context_label(result), " Gate Hierarchy\n\n"))
  print(expressalyzr::plot_gate_hierarchy(result$gs))
}
```

```{r gating-plots, fig.width=15, fig.height=8.5, dpi=90, eval=params$include_gating_plots && length(gating_context) > 0, results='asis'}
for (result in gating_context) {
  cat(paste0("\n\n### ", context_label(result), " Gate Plots\n\n"))
  pops <- flowWorkspace::gs_get_pop_paths(result$gs, path = "auto")
  gate_pops <- pops[pops != "root"]
  gate_samples <- flowWorkspace::sampleNames(result$gs)
  gate_sample_pages <- split(
    gate_samples,
    ceiling(seq_along(gate_samples) / gate_samples_per_page)
  )

  for (pop in gate_pops) {
    parent <- flowWorkspace::gs_pop_get_parent(result$gs, pop, path = "auto")
    cat(paste0("\n\n#### ", parent, " -> ", pop, "\n\n"))

    for (page_idx in seq_along(gate_sample_pages)) {
      page_samples <- gate_sample_pages[[page_idx]]
      cat(paste0("\n\n##### Wells ",
                 min((page_idx - 1L) * gate_samples_per_page + 1L,
                     length(gate_samples)),
                 "-",
                 min(page_idx * gate_samples_per_page, length(gate_samples)),
                 " of ", length(gate_samples), "\n\n"))

      p <- tryCatch({
        page_gs <- result$gs[page_samples]
        ggcyto::autoplot(page_gs, pop, bins = 35) +
          ggcyto::ggcyto_par_set(limits = "data") +
          facet_wrap(~ name, ncol = gate_plot_columns, scales = "free") +
          compact_gate_axis +
          compact_gate_y_axis +
          scale_fill_gradientn(colours = c(pal$panel, pal$fill, pal$ink)) +
          ggtitle(paste(context_label(result), parent, pop, sep = " - ")) +
          theme_qc() +
          theme(
            aspect.ratio = 1,
            strip.text = element_text(size = 8),
            axis.text = element_text(size = 7),
            axis.title = element_text(size = 9),
            panel.spacing = grid::unit(1.1, "lines")
          )
      }, error = function(e) e)

      autoplot_error <- NULL
      rendered <- FALSE
      if (!inherits(p, "error")) {
        rendered <- tryCatch({
          print(p)
          TRUE
        }, error = function(e) {
          autoplot_error <<- e
          FALSE
        })
      } else {
        autoplot_error <- p
      }

      if (!rendered) {
        fallback <- tryCatch({
          expressalyzr:::plot_template_gate_page(
            result$gs,
            template_file = result$template_file,
            pop = pop,
            samples = page_samples,
            parent = parent,
            title = paste(context_label(result), parent, pop, sep = " - "),
            max_events = params$max_events,
            ncol = gate_plot_columns
          )
        }, error = function(e) e)

        if (inherits(fallback, "error")) {
          cat(paste0("\n\n*Could not render gate plot for ",
                     context_label(result), " / ", pop, " page ", page_idx,
                     ": ggcyto: ", autoplot_error$message,
                     "; fallback: ", fallback$message, "*\n\n"))
          next
        }

        tryCatch({
          print(fallback)
        }, error = function(e) {
          cat(paste0("\n\n*Could not render gate plot for ",
                     context_label(result), " / ", pop, " page ", page_idx,
                     ": ggcyto: ", autoplot_error$message,
                     "; fallback: ", e$message, "*\n\n"))
        })
      }
    }
  }
}
```

```{r gating-plots-omitted, results='asis', eval=!params$include_gating_plots && length(gating_context) > 0}
cat(
  "Per-well gate scatter plots are omitted from this report. ",
  "Run with `include_gating_plots = TRUE` to include them."
)
```

## Compensation

```{r compensation-heatmap, fig.width=8, fig.height=6}
if (!is.null(params$so_mat)) {
  so <- params$so_mat
  so_dt <- as.data.table(as.table(so))
  setnames(so_dt, c("Source", "Detector", "Spillover"))
  so_dt[, Source := factor(Source, levels = rownames(so))]
  so_dt[, Detector := factor(Detector, levels = colnames(so))]
  so_dt[, SpilloverLabel := ifelse(
    Spillover != 0 & abs(Spillover) < 0.001,
    formatC(Spillover, format = "e", digits = 2),
    sprintf("%.3f", Spillover)
  )]

  ggplot(so_dt, aes(x = Detector, y = Source, fill = Spillover)) +
    geom_tile(colour = "white", linewidth = 0.5) +
    geom_text(aes(label = SpilloverLabel), size = 3.5) +
    scale_fill_gradient2(low = pal$blue, mid = "white", high = pal$warn,
                         midpoint = 0) +
    labs(title = "Spillover Matrix",
         subtitle = "Rows are source channels; columns are detector channels") +
    theme(axis.text.x = element_text(angle = 45, hjust = 1))
} else {
  cat("No compensation was applied for this experiment.")
}
```

---

## Files Written

```{r files-written, results='asis'}
experiment_name <- params$experiment_name
paths <- data.table(
  artifact = c("Event table", "HTML report"),
  path = file.path(params$data_path, c(
    paste0(experiment_name, ".csv"),
    paste0(experiment_name, "_report.html")
  ))
)

if (isTRUE(params$summaries_written)) {
  paths <- rbind(
    paths,
    data.table(
      artifact = c("Population summary", "Marker summary"),
      path = file.path(params$data_path, c(
        paste0(experiment_name, "_populations.csv"),
        paste0(experiment_name, "_markers.csv")
      ))
    )
  )
}

if (isTRUE(params$save_gating_set)) {
  gs_labels <- vapply(gating_context, context_label, character(1))
  gs_paths <- vapply(gating_context, function(result) {
    label <- make.names(context_template(result))
    if (length(gating_context) > 1L) {
      file.path(params$data_path, paste0("gs_", label))
    } else {
      file.path(params$data_path, "gs")
    }
  }, character(1))
  paths <- rbind(
    paths,
    data.table(artifact = paste("GatingSet", gs_labels), path = gs_paths)
  )
}

qc_kable(paths, digits = 0)
```

---

*Report generated by expressalyzr `r utils::packageVersion("expressalyzr")` &middot;
`r if(detail_mode) "Detail mode" else "Overview mode"` (`r n_samples` samples)*
